Today, any non-trivial application requires the ability to communicate over the
network. Providing a secure connection (i.e., a confidential and authenticated
connection) for the application to achieve its goals is a difficult task as it
involves correctly implementing complex protocols. Further, even if you could
provide integrity and confidentiality of data received over the network, it is
sometimes difficult to verify the benign nature of such data. Having stood the
test of time as being the most popular application for network communication,
browsers have been able to achieve network security with greater success.
However, almost all other non-browser applications have lagged behind. In this
thesis, we look at two types of applications.

First we look at tools that fetch webpages over https (such as wget) and
analyze their connection security. We then propose that these tools delegate
network security to browsers; we built a prototype version of \emph{wget} to
demonstrate the feasibility of building an application that provides security
guarantees (confidentiality, integrity, authenticity) without requiring a deep
understanding of the TLS protocol.

We then analyze package managers as they require more than just standard
network security. In particular, developers often download and execute code
from untrusted entities. Downloading and running packages over HTTPS is not
sufficient in this case. We argue for a more secure package manager, one that
can cope with nation state adversaries (who have a history of infiltrating
codebases). We describe the design of one such secure system---SPAM---that uses
the new Stellar federated Byzantine fault tolerant system.
